### 2018-10-30 Paper/revision/reviewer_replies.tex

Convergence behavior in this case depends upon the variability in the gradient of
$G(\theta)$ with respect to individual parameters, $\theta_i$ in their respective
domains. For the numerical tests and the application considered in this work, the
gradient is not observed to vary significantly in the considered domain of the
parameters. In other words, the variance of the estimator is low. 
Hence, a small number of Monte Carlo samples are able to estimate
the screening parameters. This is a common observation in many practical
applications, and therefore the proposed methodology involving an iterative
approach can yield significant computational savings.

These points have been added in the discussion in Section~6 (Summary and
Conclusion, Page 34) in the revised manuscript.

\item 
\referee{P17, Figure 3, what's the degree of the PCE used in the example? The same
question applies to Figure 6 and Figure 8.}

Sparse PCEs were constructed using least angle regression by means of UQLab software
for the two numerical tests (Borehole and the semilinear elliptic PDE),
and the reaction kinetics application in this work.  
In the borehole test case, the PCE constructed using 50 training points for the 7D, 5D, and
4D cases was found to be of degree 2, 2, and 3 respectively.  
In the semilinear elliptic PDE example, the PCE constructed using 90 training
points for the 10D and 5D cases was found to be of degree 2 and 3 respectively.
For the reaction kinetics application, the PCE constructed using 60 training points
for the 19D and 4D cases was found to be of degree 1 and 3 respectively. Note that
in each case, the degree refers to the maximal degree associated with the polynomial
basis as reported by UQLab.

@@

The captions of Figures 3, 6, and 8 have been updated to include this information.

\item
\referee{
P25, Figure 7, it seems that the rank of the parameters and the difference of
$\mu_s$ doesn't change too much over iterations. Does it indicate the initial
parameter screening  (line 1-6 in Algorithm 1) is good enough for ranking the
parameters? Can the authors plot the similar figure for other examples to see
if the iterative screening procedure does make a difference on the ranking the
parameters compared with the initial parameter screening step?}

The reviewer is correct in pointing out from Figure 7 that the initial screening step
reasonably approximates the screening metric. However, as shown in Algorithm~1,
the screening procedure involves atleast $s_\text{min}$ iterations to ensure that
the screening metric has converged. The same is observed in
Figure 5 for the semilinear elliptic PDE test case. It is also true in the borehole test
case and a similar figure has been included for this example in the revised manuscript
(Figure 2c) as suggested by the reviewer. The reason for this observation has already
been discussed in response to Comment~1 above and included in the revised manuscript.

@@

\item 
\referee{In section 4 and 5, no predictive convergence using the test data sample is
presented, only the convergence of $\epsilon_\text{LOO}$, which reuses the training data as
the validation set, is shown. This shows only the convergence of the model,
and does not necessarily indicate the (predictive) accuracy of the constructed
model, hence could lead to false conclusion. The reviewer would like to see the
convergence of $\epsilon_{L_2}$.}

As suggested by the reviewer, the plots and related discussion pertaining to the convergence 
of $\epsilon_{L_2}$ have been included for the numerical tests presented in Section 3 (Figures 3b
and 6b) and 
the chemical kinetics application presented in Section 4 (Figure 8, right). As expected, the predictive
accuracy of the surrogates is observed to increase with the number of training points in all cases. 
Additionally, the RSS is observed to be more accurate when a small number of training samples, $N$=10
is used. However, as $N$ increases the FSS is observed to be more accurate depending upon the
application.

\item 
\referee{How would the proposed approach behave when presented with severe nonlinearity
or rare events where the screening metrics could misrepresent the significance
of parameters?}

Severe non-linearity in the model output as a function of uncertain
inputs could potentially lead to a significantly large variability in
its gradient. Hence, a large number of Monte Carlo samples might be
required to estimate the screening metrics with reasonable accuracy
in that case depending upon the application. Therefore, the
computational effort is expected to increase in such cases.
Moreover, the proposed methodology aims to reduce the computational
effort pertaining to the total-effect Sobol' index, which is a
variance-based measure.  For severely nonlinear models, whose QoIs
might exhibit heavy tailed or multimodal distributions, the 
variance might not provide an adequate representation of uncertainty. 
Possible remedies for such cases 
include the so-called moment independent measures.

%it might lead to inaccurate estimates of
%%the screening metric and therefore to erroneous relative importance
%of the uncertain inputs.

### 2018-10-30 Paper/disc.tex
update ...

Based on the results presented for the test problems and the kinetics
application, the proposed framework seems quite promising in its
potential for identifying the unimportant model inputs. \rebut{In fact, in 
the numerical tests and the chemical kinetics application presented in this
work, reasonable estimates of the screening metric are obtained during the
initial screening step with a few samples. This is indicative of a small
degree of
variability in the gradient of the model output with respect to individual
parameters, and therefore, a low variance of the Monte Carlo estimator.}
These observations could be exploited to construct efficient model surrogates
in a reduced input space. However, it is important to remain cognizant
about the limitations of the framework as well. 
For instance, the quantity of interest is required to be differentiable with
respect to each parameter in the considered domain. This condition once
satisfied, enhances the accuracy of the PCE-based surrogates as well.  
\rebut{Moreover, in the presence of severe non-linearity in the model output
leading to significant variability in its gradient in the considered input domain,
the number of samples and hence, the computational effort associated with
the estimation of screening metrics would expectedly 
increase. The extent of increase in the effort would of course depend upon the
application. In the case of rare events, the variance-based methods typically
lead to inaccurate estimates of the uncertainty in the model output. Since the
methodology proposed in this work is based on reducing computational
effort associated with variance-based sensitivity analysis, specifically, the
total-effect Sobol' index, it might lead to erroneous estimates of the
screening metrics and consequently the relative importance of the
uncertain parameters.}
Additionally, the proposed framework does not
account for the existence of possible correlations between the uncertain
inputs of the model. However, while the assumption of independent
inputs is not always justified, in many cases, correlations between
inputs are not well understood a priori, and assuming mutual independence
could be reasonable at least in initial screening using DGSMs. On the other
hand, if approximate correlations are known, we recommend using a Gaussian 
process or Kriging-based surrogate since it 
provides a means for incorporating the correlation between inputs.  
Implementation to applications involving strongly correlated parameters
could enhance the applicability of the proposed framework. 
We consider that to be a potential direction for future studies related
to this work.

>>>>

Based on the results presented for the test problems and the kinetics
application, the proposed framework seems quite promising in its potential for
identifying the unimportant model inputs. \rebut{In fact, in the numerical
tests and the chemical kinetics application presented in this work, reasonable
estimates of the screening metric are obtained during the initial screening
step with a few samples. This is indicative of a small degree of variability in
the gradient of the model output with respect to individual parameters, and
therefore, a low variance of the Monte Carlo estimator.} These observations
could be exploited to construct efficient model surrogates in a reduced input
space.

While the proposed approach has attractive features, it is important to remain cognizant
about the limitations of the framework as well. 
For instance, the quantity of interest is required to be differentiable with
respect to each parameter in the considered domain. This condition once
satisfied, enhances the accuracy of the PCE-based surrogates as well.  
\rebut{Moreover, in the presence of severe non-linearity in the model output
leading to significant variability in its gradient in the considered input domain,
the number of samples and hence, the computational effort associated with
the estimation of screening metrics would expectedly 
increase. The extent of increase in the effort would of course depend upon the
application. 
Also, we note that the proposed methodology aims to reduce the computational
effort pertaining to the total-effect Sobol' index, which is a
variance-based measure.  For severely nonlinear models, whose QoIs
might exhibit heavy-tailed or multimodal distributions, the 
variance might not provide an adequate representation of uncertainty.
Possible remedies for such cases include the so-called moment independent
measures; see e.g.,~\cite{BorgonovoIooss16,IoossLemaitre15}.}
%In the case of rare events, the variance-based methods typically
%lead to inaccurate estimates of the uncertainty in the model output. Since the
%methodology proposed in this work is based on reducing computational
%effort associated with variance-based sensitivity analysis, specifically, the
%total-effect Sobol' index, it might lead to erroneous estimates of the
%screening metrics and consequently the relative importance of the
%uncertain parameters.

Additionally, the proposed framework does not
account for the existence of possible correlations between the uncertain
inputs of the model. However, while the assumption of independent
inputs is not always justified, in many cases, correlations between
inputs are not well understood a priori, and assuming mutual independence
could be reasonable at least in initial screening using DGSMs. On the other
hand, if approximate correlations are known, we recommend using a Gaussian 
process or Kriging-based surrogate since it 
provides a means for incorporating the correlation between inputs.  
Implementation to applications involving strongly correlated parameters
could enhance the applicability of the proposed framework. 
We consider that to be a potential direction for future studies related
to this work.
